Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/oopsla17.tex
Fix region definition

\begin{defn}[Region]
  A region \region{N} is an $N$-dimensional index scheme
  (\ie{}, $\region{N} \subseteq \mathcal{P}(\bz)^N)$ defined as the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}

\begin{restatable}{prop}{regionLattice}
  \label{prop:regionLattice}
  $(\region{N},\cup,\cap,\subseteq)$ is a bounded distributive lattice with top
  $\top = \bz{}^N$ and bottom $\bot = \emptyset$.
\end{restatable}
%
\begin{proof}
  Straightforward, since $\cup$ and $\cap$ are on sets (and therefore commutative,
  associative, and absorptive with each
  other). Furthermore, $\mathbb{Z}^N \cap R = R$ and $\empty \cup R =
  R$ giving the bounds. Furthermore, the lattice is distributive since
 union distributes over intersection and vice versa
\end{proof}

>>>>

\begin{defn}[Region]
  A region is an index scheme and \region{N} is the set of all regions (\ie{},
  $\region{N} \subseteq \mathcal{P}(\bz)^N)$. The set of all regions is  defined
  as the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}
%
\begin{restatable}{prop}{regionLattice}
  \label{prop:regionLattice}
  $(\region{N},\cup,\cap,\subseteq)$ is a bounded distributive lattice with top
  $\top = \bz{}^N$ and bottom $\bot = \emptyset$.
\end{restatable}
%
\begin{proof}
  Straightforward, since $\cup$ and $\cap$ are on sets (and therefore commutative,
  associative, and absorptive with each
  other). Furthermore, $\mathbb{Z}^N \cap R = R$ and $\empty \cup R =
  R$ giving the bounds. Furthermore, the lattice is distributive since
 union distributes over intersection and vice versa
\end{proof}
